### 2016-12-13 paper/evaluation.tex
Updating rq2

To evaluate the frequency of time-consuming regression tests, we
considered the 321 subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} illustrates the commands used in our
scripts to test each subject.  To avoid inflating the measured time,
we first compile the sources files (line 1) and later, we ran the
tests ignoring non-related tasks (line 3).  In addition, when we run a
subject's test suite, we operate Maven in offline mode to limit the
network access, avoiding any unnecessary package update as all
required \emph{jars} are available locally (line 2).  After the test
execution, we use a simple regular expression over the builder output
to extract the elapsed time.

@@

\Fix{To evaluate how often developers use low-level parallelism, we
considered 216 Maven projects and analyzed \Fix{x} configurations
files. For each subject, we parsed all \emph{pom.xml} files from the
project (including submodules) and searched for all \emph{surefire}
settings on each XML file. Figure \Fix{...} illustrates how a
developer can explore parallelism via Surefire settings.}

>>>>

To evaluate the frequency of time-consuming regression tests, we
considered the 312 subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} illustrates the commands used in our
scripts to test each subject.  To avoid inflating the measured time,
we first compile the sources files (line 1) and later, we ran the
tests ignoring non-related tasks (line 3).  In addition, when we run a
subject's test suite, we operate Maven in offline mode to limit the
network access, avoiding any unnecessary package update as all
required \emph{jars} are available locally (line 2).  After the test
execution, we use a simple regular expression over the builder output
to extract the elapsed time.

@@

To evaluate the  use of low-level parallelism, we considered the 91
subjects from the groups \emph{long} and \emph{medium} identified in
Section~\ref{sec:rqone}. In an initial exploration, we searched for
evidences of low-level parallelism settings on configuration files
(\ie, \emph{pom.xml}) from each subject using a semi-automated
approach: we use a script to find all subjects with evidences of
parallel settings and then we manually inspect each configuration file
to eliminate false-positives. Given a list of subjects, our script
searches recursively all \emph{pom.xml} files from the project
directory and uses the command-line tool \emph{grep} to highlight the
presence of the keywords \emph{forkMode}, \emph{forkCount}, and
\emph{parallel}. Any of these keywords exist in any possible
combination of parallel settings (see Section~\ref{sec:modes}). Before
the manual inspection, we found that 37.14\% (13 out of 35) and 62.5\%
(35 out of 56) of subjects from the \emph{long} and \emph{medium}
groups did not have any of the keywords. After the manual inspection
\Fix{...elaborate...}

\Fix{We discovered that \Fix{X}\% and \Fix{y}\%
of subjects (\emph{long} and \emph{medium}, respectively) did not have
any evidence of low-level parallelism. It is important to mention that
this result an upper bound limit since the keyword highlighted could
not be part of a real configuration (\eg, part of a comment). To
investigate further the projects reported by our script, we manually
inspected \Fix{X} configuration files to eliminate false-positives.}
\Fix{...elaborate...}
